A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-02 mt-marathon.2013/PBML_article.tex
script to replace numbers with placeholder. /Achim Ruopp

\section{File Format}
\subsection{Old Framework}
Each feature function also required a separate section in the configuration (moses.ini) file to be created, along with the code to read the new section. For example, translation models are specified in the section

  [ttable-file]

Language models in

  [lmodel-file]

Furthermore, feature function also need a separate weight section, for example, for translation models:

  [weight-t]

and language models:

 [weight-l]

New feature functions need to create and manage their own specification and sections.

@@

\subsection{New Framework}
The configuration file format has been changed to minimize the amount of boilerplate code necessary when adding new feature functions. All feature functions are declared in the configuration file in the section

  [feature]

In the fixed format

  Feature-Name [key=value]*

For example,

  KENLM factor=0 path=lm.arpa order=5

All dense weights are put into the section

  [weight]

In the fixed format

  Feature-Instance= [value]*

Similarly, weights for sparse features are in separate file referenced by the section

  [weight-file]

in the format
  Feature-Instance\_feature value

>>>>

\section{File Format}
\subsection{Old Framework}
Each feature function also required a separate section in the configuration (moses.ini) file to be created, along with the code to read the new section. For example, translation models are specified in the section
\begin{verbatim}
     [ttable-file]
\end{verbatim}
Language models in
\begin{verbatim}
     [lmodel-file]
\end{verbatim}
Furthermore, feature function also need a separate weight section, for example, for translation models:
\begin{verbatim}
     [weight-t]
\end{verbatim}
and language models:
\begin{verbatim}
     [weight-l]
\end{verbatim}
New feature functions need to create and manage their own specification and sections.

@@

\subsection{New Framework}
The configuration file format has been changed to minimize the amount of boilerplate code necessary when adding new feature functions. All feature functions are declared in the configuration file in the section
\begin{verbatim}
  [feature]
\end{verbatim}
In the fixed format
\begin{verbatim}
  Feature-Name [key=value]*
\end{verbatim}
For example,
\begin{verbatim}
  KENLM factor=0 path=lm.arpa order=5
\end{verbatim}
Similarly, all dense \emph{weights} are put into the section
\begin{verbatim}
  [weight]
\end{verbatim}
In the fixed format
\begin{verbatim}
  Feature-Instance= [value]*
\end{verbatim}
Weights for sparse features are in separate file referenced by the section
\begin{verbatim}
  [weight-file]
\end{verbatim}
in the format
\begin{verbatim}
  Feature-Instance feature value
\end{verbatim}
